
% S1: SMR, reliable, good for online services, machines, network. 
% S2: but going through network round trips for requests hurt latency of 
% services.
% S3: Traditional network layers or OS are not inherent to consensus protocols 
% because these protocols have already considered exceptional cases such as 
% packet losses and kernel failures.
% S4: We can leverage RDMA (one side read/write).
% S5: \xxx, a speed input coordination protocol that levearages fastest RDMA 
% operations.
% \xxx addresses an important challenge that practically enforce execution 
% states on systems nondeterminism such as thread nondeternimism and systems 
% resources contentions.

State machine replication (SMR) runs replicas of the same program and 
enforces same program inputs among replicas with a distributed consensus 
protocol (\eg, \paxos) despite replica failures. This strong 
fault-tolerance is particularly attractive for building a general SMR system 
for server programs. Unfortunately, to agree on inputs, traditional consensus 
protocols go through software network layers and incur prohibitively latency 
for servers. We argue that these network layers are \emph{not} inherent in SMR 
because consensus protocols can already tolerate faults in these layers (\eg, 
OS crashes). We present \xxx, a fast, general SMR system for 
server programs by leveraging Remote Direct Memory Access (RDMA). \xxx 
introduces a simple, deployable consensus protocol that exploits fastest RDMA 
one-sided write operations to agree on inputs. With this protocol, \xxx 
addresses a difficult challenge, automatically enforcing same execution states 
for active replicas, by presenting a fast, application-agnostic output checking 
protocol.

Evaluation on \nprog popular, diverse server programs (\eg, \memcached, \mysql, 
and \clamav) shows that \xxx is: (1) general, it supports these programs 
without any modification; (2) efficient, it incurs merely \overhead 
mean overhead on these programs on popular benchmarks, and it runs 6X$\sim$8X 
faster than three existing replication systems; and (3) robust, it 
recovered replica output divergence caused by a software bug in \redis, while 
\redis's own replication service missed it.

% Stat machine replication definition. Focus on networking part, 
% message passing, 
% traditional TCP/IP network. Attractive for general applications, especially 
% online services that put more and more data in memory for speed. Two challenge: 
% slow coordination; no systematic mechanism to practically enforce same 
% execution states among replicas. \xxx, efficient, application agonistic SMR 
% system. \xxx addresses the first challenge by leveraging RDMA to build an 
% speedy paxos protocol. \xxx leverages this protocol to efficiently detect 
% execution divergence that affect network outputs and perform roll back. 

% Evaluation highlights: (1) 10+ general applications, including key-value 
% stores, SQL servers, security servers, ldap servers, and multimedia servers, 
% efficient, little overhead. (2) recover from divergence caused by concurrency 
% bugs, while redis's replication system failed to detect the divergence. (3) 
% with X lines of modifications, faster than redis's own replication system by XX 
% times. 
